Draft Exploration

### 2020-04-26 draft_exploration.Rmd
working on redraft round explanation in Rmd

>>>>

Another important factor to consider when turning down the draft is how a
prospect's draft stock may change in the future. Earlier picks generally receive
larger signing bonuses, so a drop of several rounds can cost a player hundreds
of thousands of dollars in bonus money.

This graph shows the average change in draft rounds for unsigned high school picks that are redrafted.
Points above the red line indicate an improved draft stock, while those below represent a drop in draft round.
Isolating each time period, we see the curve is gradually crossing the y=0 line at earlier rounds.

This means that on average, early round picks are seeing less of a drop, or more of an improvement
in draft stock than in years past.
